---
title: "Cross Validation"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	dpi = 200,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Step 1

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - 0.3) ^ 2 + rnorm(100, 0, 0.3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```


## CV by hand

Let's get this by hand - construct a training (80%) and testing (20%) dataset.

```{r}
train_df = sample_n(nonlin_df, 80)
test_df = anti_join(nonlin_df, train_df, by = "id")

train_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```


Let's try to fit three models.

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```


Let's see the results.

```{r}
train_df %>%
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")

train_df %>%
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")

train_df %>%
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")
```


Let's make predictions and compute RMSEs.

```{r}
# Lower prediction errors mean better prediction (lower is better)
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)

test_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_point(aes(y = pred), color = "red")
```


## CV using `modelr`

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) 

cv_df %>% 
  pull(train) %>% 
  .[[1]] %>% 
  as_tibble()

cv_df = cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) %>% 
  mutate(
    linear_fits = map(.x = train, ~ lm(y ~ x, data = .x)),
    smooth_fits = map(.x = train, ~ mgcv::gam(y ~ s(x), data = .x)),
    wiggly_fits = map(.x = train, ~ mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))
  ) %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_fits, .y = test, ~ rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_fits, .y = test, ~ rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(.x = wiggly_fits, .y = test, ~ rmse(model = .x, data = .y))
  )

```

Make a box plot ...

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    names_prefix = "rmse_",
    values_to = "rmse"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```


## Try it on a real dataset

```{r}
growth_df = read_csv("data/nepalese_children.csv")
```


```{r}
growth_df %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = .3)
```

Brief aside on piecewise linear model

```{r}
growth_df =
  growth_df %>% 
  mutate(
    weight_pwl = (weight > 7) * (weight - 7)
  )
```

Compare 3 fitted models - linear model, smooth model, piecewise linear model

```{r}
linear_model = lm(armc ~ weight, data = growth_df)
pwl_model = lm(armc ~ weight + weight_pwl, data = growth_df)
smooth_model = mgcv::gam(armc ~ s(weight), data = growth_df)
```

**Linear model.**

```{r}
growth_df %>% 
  add_predictions(linear_model) %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = .3) +
  geom_line(aes(y = pred), color = "red")
```

**Piecewise linear model.**

```{r}
growth_df %>% 
  add_predictions(pwl_model) %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = .3) +
  geom_line(aes(y = pred), color = "red")
```

**Smooth model.**

```{r}
growth_df %>% 
  add_predictions(smooth_model) %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = .3) +
  geom_line(aes(y = pred), color = "red")
```


```{r}
cv_df = 
  crossv_mc(growth_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  ) 

cv_df = 
  cv_df %>% 
  mutate(
    linear_fits = map(.x = train, ~ lm(armc ~ weight, data = .x)),
    pwl_fits    = map(.x = train, ~ lm(armc ~ weight + weight_pwl, data = .x)),
    smooth_fits = map(.x = train, ~ mgcv::gam(armc ~ s(weight), data = .x))
  ) %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_fits, .y = test, ~ rmse(model = .x, data = .y)),
    rmse_pwl    = map2_dbl(.x = pwl_fits,    .y = test, ~ rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_fits, .y = test, ~ rmse(model = .x, data = .y))
  )
```

Let's look at the results.

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    names_prefix = "rmse_",
    values_to = "rmse"
  ) %>% 
  mutate(
    model = fct_inorder(model)
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```

