---
title: "Linear Models"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


Load NYC Airbnb data.

```{r}
data("nyc_airbnb")

nyc_airbnb =
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group
  ) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighbourhood, room_type)
```

## Fit the first model

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

summary(fit)
coef(fit)

fit %>% 
  broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 2)
```

Let's change reference category.

```{r}
fit = 
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough)
  ) %>% 
  lm(price ~ stars + borough, data = .)

fit %>% 
  broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 2)

fit %>% 
  broom::glance() %>% 
  select(AIC)
```

## Diagnostics

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  ylim(-250, 250)
```

## Hyoothesis testing

one coefficient (let's say `stars`).

```{r}
fit %>% 
  broom::tidy()

fit_null = lm(price ~ stars, data = nyc_airbnb)
fit_alt  = lm(price ~ stars + borough, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```


## Room type by borough

Interactions ...?

```{r}
fit =
  nyc_airbnb %>% 
  lm(price ~ stars + borough * room_type, data = .)

fit %>% 
  broom::tidy()
```

Can we fit models by borough ?

```{r}
nyc_airbnb %>% 
  nest(df = -borough) %>% 
  mutate(
    models = map(.x = df, ~ lm(price ~ stars + room_type, data = .x)),
  ) %>% 
  pull(models)

nyc_airbnb %>% 
  nest(df = -borough) %>% 
  mutate(
    models = map(.x = df, ~ lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(borough, results) %>% 
  unnest(results)
```

Quick double check ...?

```{r}
nyc_airbnb %>% 
  filter(borough == "Bronx") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()

nyc_airbnb %>% 
  filter(borough == "Queens") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()

nyc_airbnb %>% 
  filter(borough == "Brooklyn") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()
```

Mixed models.

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  lme4::lmer(price ~ stars + room_type + (1 + room_type | neighbourhood), data = .) %>% 
  broom.mixed::tidy()
```

## Binary outcomes

```{r}
baltimore_df = 
  read_csv("data/homicide-data.csv") %>% 
  filter(city == "Baltimore") %>% 
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age),
    victim_race = fct_relevel(victim_race, "White")
  ) %>% 
  select(resolved, victim_age, victim_race, victim_sex)
```

Fit a logistic regression for the binary `resolved` outcome and victim demographics as predictors.

```{r}
fit_logistic = 
  baltimore_df %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())

fit_logistic %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate)
  ) %>% 
  select(term, log_OR = estimate, OR, p.value) %>% 
  knitr::kable(digits = 3)
```

Fitted values.

```{r}
baltimore_df %>% 
  modelr::add_predictions(fit_logistic) %>% 
  mutate(fitted_prob = boot::inv.logit(pred))
```

